---
title: "HW_Bootstrap"
author: "Nan Tang"
date: "April 15, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

```{r incomes}
load("incomes.Rdat")
hist(incomes, breaks = 40, col = "skyblue")
mean(incomes) 
sd(incomes) 
quantile(incomes)
```

The histogram of incomes displayed an obvious skewed right distribution. From the relatively enormous standard deviation we can get that people's incomes vary largely in this country. One reason that causes the large sd is that there are several extreme values who earned over six hundred thousand per year.

## Question 2

```{r top5.proportion}
topQuan <- quantile(incomes, prob=0.95) 
topSum <- sum(incomes[incomes > topQuan]) 
totalSum <- sum(incomes) 
topProp <- topSum / totalSum 
sprintf("%1.4f%%", 100*topProp) 
```

We get that top 5% earner in this country owned 25.22% wealth among total incomes. If assuming everyone earns same money, top 5% people should earn 5% of total incomes.

## Question 3

```{r incomes.ci}
kSimulation <- 10000
aSampleProp <- numeric(kSimulation)
for (i in 1 : kSimulation) {
  sample <- sample(incomes, length(incomes), replace=T)
  topQuan <- quantile(sample, prob=0.95)
  topSum <- sum(sample[sample > topQuan])
  aSampleProp[i] <- topSum / sum(sample)
}
CI.value <- quantile(aSampleProp, prob = c(0.025, 0.975))
hist(aSampleProp, breaks = 30, col = "skyblue", main = "Histogram of Top 5% Earners' Incomes Among Total Incomes")
abline(v = CI.value, lwd = 2, col = "orangered")
```

## Question 4

```{r difference.ci}
bSampleProp <- numeric(kSimulation) 
for (i in 1 : kSimulation) {
  sample <- sample(incomesB, length(incomesB), replace=T)
  topQuan <- quantile(sample, prob=0.95)
  topSum <- sum(sample[sample > topQuan])
  bSampleProp[i] <- topSum / sum(sample)
}
b.CI.value <- quantile(bSampleProp, prob = c(0.025, 0.975))

#Calculate 95% interval for difference between two populations.
prop.Diff <- numeric(kSimulation)
for (i in 1 : kSimulation) {
  prop.Diff[i] <- aSampleProp[i] - bSampleProp[i]
}
diff.CI <- quantile(prop.Diff, prob = c(0.025, 0.975))

#Calculate proportion of top 5% earner's income among total income.
bTopQuan <- quantile(incomesB, prob=0.95) 
bTopSum <- sum(incomesB[incomesB > bTopQuan]) 
bTotalSum <- sum(incomesB) 
bTopProp <- bTopSum / bTotalSum 

((topProp - bTopProp) > diff.CI[1]) && ((topProp - bTopProp) < diff.CI[2]) 
```

The difference in proportion between these two income samples falls in the confidence interval of 95%, therefore, the difference is not statistically significant.

## Question 5

```{r gini.ci}
diff.gini <- numeric(kSimulation)
for(i in 1 : kSimulation) {
  aSample <- sample(incomes, length(incomes), replace=T)
  bSample <- sample(incomesB, length(incomesB), replace=T)
  diff.gini[i] <- gini(aSample) - gini(bSample)
}
diff.gini.CI <- quantile(diff.gini, prob = c(0.05, 0.95))
diff.gini.CI
```

90% confidence interval of difference between two populations' gini coefficient is 0.0465 to 0.1027.

